cardinalR: Generating interesting high-dimensional data structures

### 2025-09-05 paper-cardinalR.Rmd
Updated Table 1

```{r}
main_tb <- tibble(arg = c("n",
                          "p",
                          "k",
                          "loc",
                          "scale",
                          "shape",
                          "rotation",
                          "is_bkg"), 
                        exp = c("A numeric vector representing the number of points in each cluster.",
                                "A numeric value representing the number of dimensions.",
                                "A numeric value representing the number of clusters.",
                                "A numeric matrix representing the locations/centroids of clusters.",
                                "A numeric vector representing the scaling factors of clusters.",
                                "A character vector representing the shapes of clusters.",
                                "A numeric list which contains plane and the corresponding angle along that plane for each cluster.",
                                "A Boolean value representing the background noise should exist or not."))
```

```{r main-tb-html, eval=knitr::is_html_output()}
main_tb |> 
  kable(caption = "The main arguments for `gen_multicluster()`.", col.names = c("Argument", "Explanation")) 
```

```{r main-tb-pdf, eval=knitr::is_latex_output()}
main_tb |> 
  kable(caption = "The main arguments for gen\\_multicluster().", format="latex", col.names = c("Argument", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

>>>>

```{r}
main_tb <- tibble(arg = c("n",
                          "p",
                          "k",
                          "loc",
                          "scale",
                          "shape",
                          "rotation",
                          "is_bkg"),
                  type = c("numeric (vector)",
                           "numeric",
                           "numeric",
                           "numeric (matrix)",
                           "numeric (vector)",
                           "character (vector)",
                           "numeric (list)",
                           "boolean"),
                        exp = c("Number of points in each cluster.",
                                "Number of dimensions.",
                                "Number of clusters.",
                                "Locations/centroids of clusters.",
                                "Scaling factors of clusters.",
                                "Shapes of clusters.",
                                "Plane and the corresponding angle along that plane for each cluster.",
                                "Background noise should exist or not."))
```

```{r main-tb-html, eval=knitr::is_html_output()}
main_tb |> 
  kable(caption = "The main arguments for `gen_multicluster()`.", col.names = c("Argument", "Type", "Explanation")) 
```

```{r main-tb-pdf, eval=knitr::is_latex_output()}
main_tb |> 
  kable(caption = "The main arguments for gen\\_multicluster().", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "4cm") |>
  column_spec(3, width = "8cm")
```

### 2025-09-05 paper-cardinalR.tex
Updated Table 1

\caption{\label{tab:main-tb-pdf}The main arguments for gen\_multicluster().}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Argument & Explanation\\
\midrule
n & A numeric vector representing the number of points in each cluster.\\
p & A numeric value representing the number of dimensions.\\
k & A numeric value representing the number of clusters.\\
loc & A numeric matrix representing the locations/centroids of clusters.\\
scale & A numeric vector representing the scaling factors of clusters.\\
\addlinespace
shape & A character vector representing the shapes of clusters.\\
rotation & A numeric list which contains plane and the corresponding angle along that plane for each cluster.\\
is\_bkg & A Boolean value representing the background noise should exist or not.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:main-tb-pdf}The main arguments for gen\_multicluster().}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Argument & Type & Explanation\\
\midrule
n & numeric (vector) & Number of points in each cluster.\\
p & numeric & Number of dimensions.\\
k & numeric & Number of clusters.\\
loc & numeric (matrix) & Locations/centroids of clusters.\\
scale & numeric (vector) & Scaling factors of clusters.\\
\addlinespace
shape & character (vector) & Shapes of clusters.\\
rotation & numeric (list) & Plane and the corresponding angle along that plane for each cluster.\\
is\_bkg & boolean & Background noise should exist or not.\\
\bottomrule
\end{tabular}
\end{table}
